LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-02-17 src/ms.tex
adding ambition for lw 2.0

\referee{We note that the amplitude modulation is only implemented in \lw{} for quasi-circular binaries to remain consistent with the calculation in \cite{Cornish2003}. Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the scope of \lw{}.}

>>>>

\referee{We note that the amplitude modulation is only implemented in \lw{} for quasi-circular binaries to remain consistent with the calculation in \cite{Cornish2003}. Since the expected use case of LEGWORK is estimation of the detectability of large populations of mHz stellar-remnant binaries, for which predictions are uncertain by orders of magnitude in some cases, an extension of \cite{Cornish2003} which includes eccentric binaries is out of the current scope of \lw{}.}
